% !TEX program = xelatex
%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% fontspec allows you to use TTF/OTF fonts directly
\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}

% Use a system font that supports Vietnamese (e.g., Arial, Times New Roman, or Calibri)
% If you have specific OTF files, you can uncomment the lines below
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}
\setmainfont{TeX Gyre Termes} % Professional replacement for Times New Roman, available in TeX Live

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

%for social icons
\usepackage{fontawesome5}
\usepackage{fancyhdr}

% Footer configuration
\pagestyle{fancy}
\fancyhf{} % Clear all headers and footers
\renewcommand{\headrulewidth}{0pt} % Remove the horizontal line at the top
\fancyfoot[R]{\footnotesize Personal proof: \href{https://drive.google.com/drive/folders/1xuzW6nMIUNZ8DPcMAYzBtpsdtBfsKtxs?usp=sharing}{Google Drive}}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages (we use fancy style now for the footer)
\pagestyle{fancy} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Doan Tri Hung} \\[7.5pt]
\href{https://github.com/hungdt31}{\raisebox{-0.05\height}\faGithub\ hungdt31} \ $|$ \ 
\href{https://www.linkedin.com/in/hungdt31}{\raisebox{-0.05\height}\faLinkedin\ doantrihung} \ $|$ \ 
\href{https://dthretro-portfolio.vercel.app}{\raisebox{-0.05\height}\faGlobe \ Portfolio} \ $|$ \ 
\href{mailto:koikoidth12@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ koikoidth12@gmail.com} \ $|$ \ 
\href{tel:0394529624}{\raisebox{-0.05\height}\faMobile \ 0394529624} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
As a \textbf{Frontend Developer}, I specialize in building highly responsive and interactive web applications with a focus on delivering exceptional user experiences through clean and maintainable code. I leverage modern frontend technologies and industry best practices to create high-performance interfaces, ensuring accessibility and seamless cross-platform compatibility.

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Bachelor's Degree (GPA: 3.5/4.0)} & \textbf{2022 -- Present} \\
VNU-HCMUT, Ho Chi Minh City University of Technology  & Ho Chi Minh City, Vietnam \\[6pt]
\textbf{High School Diploma (Physics-oriented Program)} & \textbf{2019 -- 2022} \\
Bac Lieu High School For The Gifted & Bac Lieu, Vietnam \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{English} &  \normalsize{TOEIC Listening and Reading 710} \vspace{0.1cm} \\
\textbf{Programming Languages}  &  \normalsize{TypeScript, JavaScript, C++, SQL, PHP, Python, Java.} \vspace{0.1cm} \\
\textbf{Databases}  &  \normalsize{Microsoft SQL Server, MySQL, PostgreSQL, MongoDB.} \vspace{0.1cm} \\
\textbf{Frameworks} &  \normalsize{ExpressJS/ NodeJS, Next.js, NestJS, Expo.} \vspace{0.1cm} \\
\textbf{Libraries} &  \normalsize{React.js, React Native, Redux, Shadcn/ui, MUI/ Material UI.} \vspace{0.1cm} \\
\textbf{Others} &  \normalsize{HTML/CSS, Prisma, Docker, Supabase, Git, Figma, Agile Scrum.}\\
\end{tabularx}

%Experience
\section{Work Experience}

% \begin{jobshort}{Designation}{Jan 2021 - present}
% long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width
% \end{jobshort}


\begin{joblong}{mgm technology partners Vietnam}{Dec 2025 - Feb 2026}
\item Internship $|$ Software Engineer
\item Build a platform for English writing featuring a rich text editor, real-time AI-powered feedback and suggestions, easy sharing of writing pieces, and a community space to exchange ideas and improve English writing skills.
\item Ho Chi Minh City, Vietnam, On-site
\end{joblong}

\begin{joblong}{Apollogix, Inspiring Innovation Delivering Solutions}{Jun 2025 - Aug 2025}
\item Internship $|$ Frontend Developer
\item Developed the frontend of a task management system for a logistics enterprise, focusing on intuitive UI design, responsive layouts, and a seamless user experience to support efficient workflow tracking and team collaboration.
\item Ho Chi Minh City, Vietnam, On-site
\end{joblong}

% \begin{joblong}{HCMUT EE Machine Learning \& IoT Lab}{Oct 2024 - Present}
% \item Member of Lab - Web Developer
% \item Facilitated the dissemination of AI/ML knowledge to diverse professional audiences, resulting in improved team proficiency and knowledge sharing across numerous sessions.
% \item Ho Chi Minh City, Vietnam, On-site
% \end{joblong}

%----------------------------------------------------------------------------------------
%	CERTIFICATE
%----------------------------------------------------------------------------------------
\section{Certificate}
\begin{joblong}{SDWS Training}{Axon Active - Agile Software Development Company}
\item Issued Jun 2025 $|$ \href{https://verified.sertifier.com/en/verify/35754468941115/}{Credential Link}
\item Introduces the basics of Agile and Scrum: key values and practices for adaptability, main roles (Product Owner, Development Team, Scrum Master), and core artifacts (Product Backlog, Sprint Backlog, Increment) that guide and deliver project outcomes.
\end{joblong}

%Projects
\section{Projects}

% \begin{tabularx}{\linewidth}{ @{}l r@{} }
% \textbf{Some Project} & \hfill \href{https://some-link.com}{Link to Demo} \\[3.75pt]
% \multicolumn{2}{@{}X@{}}{long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width}  \\
% \end{tabularx}

\begin{joblong}{{\shortstack[l]{SmartDKDH -- Home Automation System\\ Frontend Developer $|$ 5-member team}}}{{\shortstack[r]{Multidisciplinary Project\\ Feb 2025 -- Apr 2025}}}
\item \textbf{Description:} IoT-based home automation system enables users to monitor and control household devices via a mobile app, integrating with the Adafruit IO platform for real-time control and sensor data monitoring.
\item \textbf{Responsibilities:} Developed and iterated React Native / Expo mobile app, implementing authentication flows, device control (lights, fans), and real-time sensor dashboards. Integrated REST APIs, WebSocket streams, and Adafruit IO to ensure consistent device state synchronization. Built user and device management screens with full CRUD operations aligned with backend contracts. Collaborated on integration testing, debugging cross-service issues, and improving UI/UX consistency.
\item \textbf{Technologies:} React Native, Expo, WebSocket, FastAPI, MongoDB.
\item Repository: \href{https://github.com/Enigmask22/SmartDKDH}{github.com/Enigmask22/SmartDKDH}
\end{joblong}

\begin{joblong}{{\shortstack[l]{Day Mood - Mood Journaling App\\ Full-stack Developer $|$ 4-member team}}}{{\shortstack[r]{Mobile Application Development\\ Feb 2025 -- May 2025}}}
\item \textbf{Description:} Cross-platform mood journaling application supporting emotion tracking, activity logging, and secure media attachments to enhance user self-awareness.
\item \textbf{Responsibilities:} Built core React Native features for journaling flows, input handling, and media attachments. Designed and implemented backend services using NestJS with Prisma ORM and PostgreSQL, covering authentication, journal records, and file upload pipelines. Designed UI/UX flows in Figma and published visual case study on Behance to align design and implementation. Participated in architecture discussions, bug fixing, and release preparation.
\item \textbf{Technologies:} React Native, NestJS, Prisma, PostgreSQL, JWT, Figma.
\item Frontend: \href{https://github.com/Enigmask22/DayMood}{github.com/Enigmask22/DayMood}
\item Backend: \href{https://github.com/Enigmask22/DayMood-Backend}{github.com/Enigmask22/DayMood-Backend}
\item Behance: \href{https://www.behance.net/gallery/222654927/DayMood}{https://www.behance.net/gallery/222654927/DayMood}
\end{joblong}

\begin{joblong}{{\shortstack[l]{ATS -- Applicant Tracking System\\ Full-stack Developer}}}{{\shortstack[r]{Personal Project\\ Mar 2025 -- Present}}}
\item \textbf{Description:} A full-stack recruitment management platform designed to streamline the application process for both candidates and employers, featuring comprehensive job tracking and candidate management.
\item \textbf{Responsibilities:} Architected and built the entire application from scratch using Next.js 16 (App Router) and React 19. Implemented a robust candidate tracking system with a centralized dashboard for managing job listings, applications, and candidate profiles. Integrated Appwrite for scalable storage and Resend for automated email notifications and implemented Shadcn UI with Tailwind CSS 4 for a modern, responsive UI. Refactored API logic to React Query hooks to improve state management and data fetching efficiency.
\item \textbf{Technologies:} Next.js 16, React 19, TypeScript, Prisma, Appwrite, Resend, Tailwind CSS 4.
\item \textbf{Repository:} \href{https://github.com/hungdt31/ats}{github.com/hungdt31/ats}
\end{joblong}

%----------------------------------------------------------------------------------------
%	ACTIVITIES
%----------------------------------------------------------------------------------------
\section{Activities}
\begin{tabularx}{\linewidth}{@{}l X@{}}
THE INNOVATION WINNER PRIZE of The Explosion Competition 2022. \vspace{0.1cm} \\
Final Round of the IT Contest Code Your Future 2024 held by CJ OLIVENETWORKS VINA. \vspace{0.1cm} \\
THE SPRING VOLUNTEER CAMPAIGN in 2024 and 2025. \\
\end{tabularx}

\vfill
% \center{\footnotesize Last updated: \today}

\end{document}
